Template Master's Thesis

### 2023-08-18 paper.tex
Update discussion

Throughout our analysis, we successfully applied three clustering heuristics to our address set, utilizing the available on-chain data. These heuristics were self-authorization, node embedding, and LAND transfers. In the following discussion, we will examine each of these approaches step-by-step.

%%%%%%%%%%%%%%%%%%%%
Self-authorization is a straightforward technique, but results in very few identified address clusters. This is because it requires a highly specific on-chain behavior, which is rarely observed in practice. In particular, approvals are seldom used to authorize another externally owned account one might own. We also encountered a significant number of false-positives due to non-standard implementations. After excluding these instances, we identified a total of 15 entities consisting of 35 addresses. This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses. In his analysis of transaction data up to Ethereum block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
%%%%%%%%%%%%%%%%%%%%

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. \newline
Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and simultaneously analyze data from Polygon and Ethereum. The main reason is previous implementations' different settings and research questions. \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives. \newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with previous findings, which identified Diff2Vec as the most effective method out of the three. \newline
Determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ... A possible explanation is that Role2Vec ... % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size, possible flaws in the evaluation via average rank and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes representing addresses. Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec. Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged. \newline
Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between various ground truth pairs exhibit significant variation. \newline
We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors. Unfortunately, these modifications did not yield improvements. Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

>>>>

Throughout our analysis, we successfully applied three heuristics to cluster our address set, while utilizing on-chain data. In the following discussion, we will examine each of the approaches step-by-step. %The heuristics we applied were self-authorization, node embedding, and LAND transfers.

%%%%%%%%%%%%%%%%%%%%
Implementing the self-authorization heuristic is straightforward, but results in very few identified address clusters. This is because it requires a highly specific on-chain behavior, which is rarely observed in practice. In particular, approvals are seldom used to authorize another externally owned account one might own. We also encountered a significant number of false-positives due to non-standard implementations. After excluding these instances, we identified a total of 15 entities consisting of 35 addresses. This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses. In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
%%%%%%%%%%%%%%%%%%%%

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. \newline
Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions. We construct the network graph based on the asset transfers within our address set and simultaneously analyze Polygon and Ethereum data. \newline
Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction. \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.

Moreover, we validated our approach and found better results in terms of average rank of ENS pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions. \newline
%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
We applied three node embedding algorithms that showed strong performance in the experiments by \cite{Beres2020} and assessed their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.  This diverges from previous findings that favored Diff2Vec as the most effective of the three methods. \newline
Determining why one approach outperforms another is complex. Diff2Vec and DeepWalk, both neighborhood-preserving algorithms, mainly capture node proximity. However, as noted by ..., this does not necessarily imply similarity, especially when addresses may frequently interact without being controlled by the same entity. In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar network roles. In our scenario, network position or role may better represent similarity and structural relatedness among nodes in our evaluation sample. Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods. \newline
Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 addresses. Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec. Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged. \newline
Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between various ground truth pairs exhibit significant variation. \newline
We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors. Unfortunately, these modifications did not yield improvements. Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.
